Union and intersection contracts are hard, actually

### 2021-07-24 paper.tex
Dimoulas papers, reformatting
Revision: review of Castagna et al. (draft)

Castagna et al.~\cite{gradualCastagna} introduce a gradual type system based on
so-called set-theoretic types~\cite{SetTheoreticTypes}.  Set-theoretic types
feature unions, intersections, negation types together with a notion of
subtyping. This work adheres to the \emph{static first school} (see
~\cite{practiceTheoryGrad}) of gradual typing: the reason for gradual types is
to allow for a less precise type information. It follows that their goals and
constraints are somehow different, resulting in the absence of first-class
contracts. As for any gradual type system, they do have to implement
casts~---~that are very close to contracts~---~for unions and
intersections, but these casts
are neither visible nor available to the programmer. Obviously, no contracts
mean no user-defined contracts as well.

>>>>

Castagna and Lanvin~\cite{CastagnaLanvinGradualUnionIntersection} introduce a
gradual type system based on so-called set-theoretic
types~\cite{SetTheoreticTypes}.  Set-theoretic types feature unions,
intersections, negation types together with a notion of subtyping. This work
adheres to the \emph{static first school} (see ~\cite{practiceTheoryGrad}) of
gradual typing: the reason for gradual types is to allow for a less precise type
information. It follows that their goals and constraints are somehow different,
resulting in the absence of first-class contracts. As for any gradual type
system, they do have to implement casts~---~that are very close to
contracts~---~for unions and intersections, but these casts are neither visible
nor available to the programmer. Obviously, no contracts mean no user-defined
contracts as well.

Castagna and Lanvin use abstract interpretation to derive the semantics of
unions and intersections. In their own words, "the resulting definitions are
quite technical and barely intuitive but they have the properties we seek for
[\ldots]".  This makes any comparison with the co-inductive semantics of Kiel
and Thiemann rather difficult. Castagna et al.~\cite{gradualCastagna} build on
Castagna and Lanvin to add polymorphism in the picture. However, it is at the
price of restricting the union and intersection part: it is not possible to
assign intersection types to a function anymore.
